|

### 2019-12-17 article/article.Rmd
add revisions

# Load scripts
lapply(pkgs, require, character.only = T)
rm(pkgs, install_if_not)
load("tdp.RData")
```

@@

We also conducted two manipulation checks and analysed the number of TDP app
downloads by municipality and over time. Figure \ref{fig:manipulation1}
displays the results and indicates that the treatment has good territorial
variability. There are `r length(unique(ga$municipality[ga$phase1==1]))`
downloads in the 
`r length(unique(impact_evaluation_phase1$municipality[impact_evaluation_phase1$treat=='Treatment']))`
municipalities in the treatment condition. Downloads peak during the Facebook
TDP campaign, launched in October 2017, then diminish in the following months.

@@

\newpage
The second intervention is similar to intervention 1 in all but three
characteristics. First, the TDP app was **then** available for both Android and
iOS devices. Second, we randomised the intervention at the school level, with
`r as.numeric(table(impact_evaluation_phase2$treat)[1])` control and 
`r as.numeric(table(impact_evaluation_phase2$treat)[2])` treatment units. We
used blocked randomisation stratified by Brazilian states, school construction
status (under construction, stopped, unfinished), and whether the municipality
spent more on school construction that the distribution median. Finally, the
intervention period lasted from August 2018 to February 2019.

Balance tests and manipulation checks were also successful for intervention 2.
In total, `r length(unique(ga$municipality[ga$phase2==1]))` municipalities
downloaded the app. There is about 1,000 user downloads in August 2018, right
after intervention 2 starts, and a second spike around December. The number of
downloads is smaller in this second intervention as there was no associated
social media campaign in that period.

@@

**(Short paragraph on whether the app has worked)**

@@

**The electoral cycle might have decreased the potential effect of the treatment,
too. As the experiment was fielded right after Brazil's municipal elections,
incumbents might have disregarded the requests because they did not see the
demands as politically costly in the short run. Having just taken office,
mayors might have focused their attention to the formation of government
coalitions or to budget concerns. **

~~Moreover, it is possible that a mobile app like TDP is simply not sufficient
to promote collective action. @raffler2018weakness [29] point out several
reasons why information interventions does not lead to higher pressure on
public agents, such as citizens' apathy towards their ability to make public
agents accountable, lack of official channels to support popular demands, or
that constituents have more pressing needs than monitoring representatives.
Furthermore, individuals may also believe they are better off by free-riding on
other users of the TDP app, thus reaping the benefits of having faster school
constructions without incurring personal costs [@olson1965logic].~~

>>>>

# Load scripts
lapply(pkgs, require, character.only = T)
rm(pkgs, install_if_not)
load("tdp.RData")

# Disable scientific notation
options(scipen = 999)
```

@@

We also conducted two manipulation checks and analysed the number of TDP app
downloads by municipality and over time. Figure \ref{fig:manipulation1}
displays the results and indicates that the treatment has good territorial
variability. There are `r length(unique(ga$municipality[ga$phase1==1]))`
downloads in the 
`r format(length(unique(impact_evaluation_phase1$municipality[impact_evaluation_phase1$treat=='Treatment'])),
big.mark = ",")` municipalities in the treatment condition. Downloads peak
during the Facebook TDP campaign, launched in October 2017, then diminish in
the following months. **Overall, 
`r format(sum(ga$novos_usuarios[ga$phase1==1]), big.mark = ",")` users
downloaded the app in phase one.**

@@

\newpage
The second intervention is similar to intervention 1 in all but three
characteristics. First, the TDP app was **then** available for both Android and
iOS devices. Second, we randomised the intervention at the school level, with
`r as.numeric(table(impact_evaluation_phase2$treat)[1])` control and 
`r format(as.numeric(table(impact_evaluation_phase2$treat)[2]), big.mark = ",",
scientific = FALSE)` treatment units. We used blocked randomisation stratified
by Brazilian states, school construction status (under construction, stopped,
unfinished), and whether the municipality spent more on school construction
that the distribution median. Finally, the intervention period lasted from
August 2018 to February 2019.

Balance tests and manipulation checks were also successful for intervention 2.
In total, `r length(unique(ga$municipality[ga$phase2==1]))` municipalities
downloaded the app. There is about 1,000 user downloads in August 2018, right
after intervention 2 starts, and a second spike around December. 
**The app gained 
`r format(sum(ga$novos_usuarios[ga$phase1==0]), big.mark = ",")` new users
during intervention 2. The number of downloads is smaller in this second
intervention as there was no associated social media campaign in that period.**

@@

**Data from Google Analytics suggest that users did engage with the TDP app. On
average, each user launched `r format(round(mean(as.numeric(gsub('\\.', '',
ga2$visualizacoes_de_tela))), 2), big.mark = ",")` app sessions, which
indicates their interest in the application. In total, the app had 
`r format(sum(as.numeric(gsub('\\.', '', ga2$visualizacoes_de_tela))),
big.mark = ",", scientific = F)` screen visualisations, with an average of 
`r round(mean(as.numeric(gsub(',', '.', ga2$telas_sessao))), 2)` screen
visualisations per session.**

@@

**The electoral cycle might also have decreased the potential effect of the
treatment. As the experiment was fielded right after Brazil's municipal
elections, incumbents might have disregarded the requests because they did not
see the demands as politically costly in the short run. Having just taken
office, mayors might have focused their attention to the formation of
government coalitions or to budget concerns. Future research may evaluate how
electoral dynamics interact with citizen oversight, potentially by replicating
informational experiments in different stages of the political cycle.**

\sout{Moreover, it is possible that a mobile app like TDP is simply not
sufficient to promote collective action. Raffler et al (2018, 29) point
out several reasons why information interventions does not lead to higher
pressure on public agents, such as citizens' apathy towards their ability to
make public agents accountable, lack of official channels to support popular
demands, or that constituents have more pressing needs than monitoring
representatives. Furthermore, individuals may also believe they are better off
by free-riding on other users of the TDP app, thus reaping the benefits of
having faster school constructions without incurring personal costs (Olson
1965).}
